Getting to the point of writing this dissertation has been a long process\footnote{This paper captures the thesis writing process exceptionally well \cite{Upper1974.JABA.7.497}.}.
Although my name is on the title page, by no means could I have accomplished any of it on my own. 
Echoing the sentiment expressed in \cite{DeSalvo2015.PhD}, including everyone who helped me along this journey would markedly increase the page count of this thesis so what follows below is an incomplete list.

% Rice
I would like to start off by thanking my advisers Dr. F. Barry Dunning and Dr. Thomas C. Killian.
To Barry for his wisdom and enthusiasm, pushing me to be better by asking insightful (and often challenging) questions and always being excited to discuss the latest developments.
To Tom for keeping me focused on what's important and trusting me to develop new tools and techniques outside of what has been previously tried in the lab.
And to both of them for always providing guidance when I was lost and support when I made a mistake.
I would also like to thank Dr. Shuhei Yoshida who not only provided me with many calculations but also helped me understand the theory behind them. 

Building a new experiment has been intimidating but I couldn't have asked to work alongside anyone better than (Dr.) Francisco Camargo and (soon-to-be Dr.) Joe Whalen in sharing the challenges and successes. 
To Francisco for keeping everything moving forward and the data rolling in and to Joe for being an insane physicist who always seems to have the answer. 
To Soumya Kanungo, as the first student on the Rydberg experiment who didn't have the luxury of building the various systems, it's been amazing watching the rapid progression you made from an inexperienced first-year graduate student to leading the experiment.
Handing the Rydberg experiment off to you, Haad Rathore, and Yi Lu, I have no doubt that you three will be able to overcome any obstacles you encounter and I can only hope that the apparatus treats you well. 
To (Dr.) Jim ``James'' Aman and (Dr.) Thomas Langin, we started graduate school together working through problem sets and we all (eventually) graduated and I'm excited to see where both of you end up.
I would also like to thank everyone else in the Killian\footnote{Dr. Brian DeSalvo, Dr. Patrick McQuillen, Joshua Hill, Grant Gorman, MacKenzie Warrens.} and Dunning\footnote{Dr. Shuzen Ye, Dr. Xinyue ``Vivian'' Zhang, Dr. Michael Kelley, Dr. Sitti Buathong, Gavin Fields, and Robert Brienza.} labs who made the years fly by.

% SMCM
As an undergraduate at St. Mary's College of Maryland (SMCM), I had never considered pursuing a graduate degree until Dr. Joshua Grossman gave me the opportunity experience physics research.
His breadth and depth of knowledge is what lead me to develop an interest in atomic, molecular, and optical (AMO) physics (after trying my hand at computational physics). 
He has also been a constant source of advice and guidance in the years since I graduated for which I am grateful.
I would also like to thank my Research Experiences for Undergraduates (REU) adviser Dr. Daniel Elliott at Purdue University for giving me the opportunity to spend a summer in his lab working with his graduate students\footnote{Now Dr. John Lorenz, Dr. Adeel Altaf, Dr. Dionysios Antypas, and Dr. Sourav Dutta.} seeing what graduate school in an AMO lab is really like. 

I would also like to acknowledge several other professors for which I am grateful. 
At Rice, I would like to thank Dr. Junichiro Kono and Dr. Han Pu for serving on my master's and doctoral committees, respectively.
And to Dr. Randy Hulet and Dr. Kaden Hazzard who taught me much of what I know about atomic physics and quantum optics. 
In addition, Dr. Lam Yu and Dr. Stan Dodds always made for interesting conversations. 
At SMCM, I would also like to thank Dr. Erin DePree. 

Lastly, but most importantly, I would like to thank my father Zuyi Ding.
You singlehandedly raised me from when I was a child and provided everything I could have asked for.
None of this would have been possible without the sacrifices you made and I hope this gives you something to be proud of. 